---
title: "HW03"
author: "Elena Burkey"
date: "2/22/2021"
output: 
  html_document:
    theme: paper
  github_document: default
---



```{r setup, include = False}
knitr::opts_chunk$set(echo = TRUE)
dictionary <- readr::read_csv("green_dictionary.csv")
green_data <- readr::read_csv("green_data.csv")
library(tibble)
library(ggplot2)
library(tidyverse)
library(gridExtra)
library(reshape2)
library(ggdist)
```

# Homework 03

You will analyze data looking at the relationship between **green reputation** and three personality traits--**compassion**, **intellectual curiosity**, and **openness to experiences**.
The dataset includes data from **students** and **non-students**.

# 1)
Inspect the item responses (e.g., with graphs or by summarizing distinct values).     Is anything unusual?

```{r}
as_tibble(green_data)
```

```{r}
green_data.melt <- melt(green_data, measures.var = across (c:green1:open10))
```

- Brings the data from columns to rows by using the melt function and will show everything in the data set in such a manner that it's easily seen if there are repeating values or if anything is off with the data set 

```{r}
summary(green_data.melt)
```

- It can be seen in the data set that there are values that do not seem to fit into the set such as -99 and that there are repeated values

```{r}

```

#2
Compute total scores for the four scales. 
    Recode variables as needed.

```{r}
reverse_recode <- dictionary %>%
  
```


  3. Rescale the variables so that they go from 0-100 instead of the original range.
     Name the recaled variables `*_pomp`.
  4. Make plots that illustrate the distributions of the 4 POMP-scored variables.
  5. Make scatterplots showing the relationships between **green reputation** and each personality trait.
     Include trend lines for **students** and **non-students**.
     What do these plots show?
  6. Compare **green reputation** for students and non-students using a **rainfall plot** (bar + density + data points).
  7. Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.
  
In your assignment, prepare an RMarkdown file that includes both the coding and (for 4-7) narrative descriptions of your results.
