---
title: "HW03"
author: "Elena Burkey"
date: "2/22/2021"
output: 
  github_document: default
  html_document:
    theme: paper
---



```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
dictionary <- readr::read_csv("green_dictionary.csv")
green_data <- readr::read_csv("green_data.csv")
library(tibble)
library(ggplot2)
library(tidyverse)
library(gridExtra)
library(reshape2)
library(ggdist)
library(psychTools)
```

# Homework 03

You will analyze data looking at the relationship between **green reputation** and three personality traits--**compassion**, **intellectual curiosity**, and **openness to experiences**.
The dataset includes data from **students** and **non-students**.

## 1)
Inspect the item responses (e.g., with graphs or by summarizing distinct values).     Is anything unusual?

```{r}
as_tibble(green_data)
```

- Looking at the data set it seems that there are quite a bit of NA values. 

```{r}
green_data.melt <- melt(green_data, measures.var = across (c:green1:open10))
```

- Brings the data from columns to rows by using the melt function and will show everything in the data set in such a manner that it's easily readable. 

```{r}
summary(green_data.melt)
```

- It can be seen in the data that -99 is being said to be the minimum value and therefore needs to be recoded. 

```{r}
ggplot(green_data.melt) +
  aes(X = id, Y = value)
  geom_point(alpha = 0.1) +
  theme_bw()
```

## 2)
Compute total scores for the four scales. 
    Recode variables as needed.

```{r}
reversed <- dictionary %>%
  filter(Keying == -1 | Keying == -2)%>%
  pull(Item)
```

```{r recode}
Green_New <- green_data %>%
  mutate(student = recode (student, "1" = "Not_Student", "2" = "Student", .missing = "No_Response", .default = "Unknown")) %>%
  select(id, student)
```

```{r}
green_data %>%
  mutate(across(everything(),
                ~ na_if(.x, -99)))
```

- Taking away  the -99 values and coding them into missing data 

```{r}
Green_R <- green_data %>%
  mutate(across(all_of(reversed), 
                ~ recode(.x, 
                         "5" = 1,
                         "4" = 2,
                         "3" = 3,
                         "2" = 4,
                         "1" = 5)))
```

- Recoded the data to organize it properly and categorize it in a way that is more clear 


```{r}
Green_Calculations <- green_data %>%
  rowwise() %>%
  mutate(tot_green = sum(c_across(green1 : green5), na.rm = TRUE),
         tot_comp = sum(c_across(comp1 : comp10), na.rm = TRUE), 
         tot_intel = sum(c_across(intel1 : intel10), na.rm = TRUE),
         tot_open = sum(c_across(open1 : open10), na.rm = TRUE))
```

 
## 3)
Rescale the variables so that they go from 0-100 instead of the original range.
     Name the recaled variables `*_pomp`.

```{r}
Green_Rescale <- green_data %>%
  mutate(across(all_of(reversed), ~ recode(.x, "1" = 0, "2" = 25, "3" = 50, "4" = 75, "5" = 100), .names = "{.col}_pomp")) %>%
  rowwise() %>%
  mutate(
    green_pomp = sum(c_across(green1 : green5), na.rm = TRUE),
    comp_pomp = sum(c_across(comp1 : comp10), na.rm = TRUE), 
    intel_pomp = sum(c_across(intel1 : intel10), na.rm = TRUE),
    open_pomp = sum(c_across(open1 : open10), na.rm = TRUE))
```

- I recoded the variables so that it went from  0-100 and then rescaled the items. 
     
##4)
Make plots that illustrate the distributions of the 4 POMP-scored variables.

```{r}
ggplot(Green_Rescale) +
  aes(x = green_pomp) +
  geom_histogram(fill = "green", fill = "grey") +
  theme_bw() +
  ggtitle("Green Data")
```

```{r}
ggplot(Green_Rescale) +
  aes(x = comp_pomp) +
  geom_histogram(fill = "purple", fill = "grey") +
  theme_bw() +
  ggtitle("Comp Data")
```

```{r}
ggplot(Green_Rescale) +
  aes(x = intel_pomp) +
  geom_histogram(fill = "red", fill = "grey") +
  theme_bw() +
  ggtitle("Intel Data")
```

```{r}
ggplot(Green_Rescale) +
  aes(x = open_pomp) +
  geom_histogram(fill = "blue", fill = "grey") +
  theme_bw() +
  ggtitle("Open Data")
```

- Looking at the different graphs, all of the graphs except for the Green Data graph were not equally distributed. 

##5)
Make scatterplots showing the relationships between **green reputation** and each personality trait.
     Include trend lines for **students** and **non-students**.
     What do these plots show?
```{r} 
Green_Rescale %>%
  mutate(student = recode(student, "1" = "Not_Student", "2" = "Student"))

ggplot(na.omit(Green_Rescale))+
  aes(x = green_pomp, y = comp_pomp, fill = student, color = student) + 
  geom_point()
```

- In this section I am comparing the relationship between the green data against the personality traits. I am also using na.omit to remove all of the incomplete cases within the data set. 

##6)
Compare **green reputation** for students and non-students using a **rainfall plot** (bar + density + data points).

```{r} 
ggplot(na.omit(Green_Rescale)) +
  aes(x = green_pomp, fill = student, color = student) +
  geom_jitter(height = .30) +
```
 
#7) 
Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.
  
```{r} 

```
